---
title: "Covid and Air Quality"
author: "Bowie Lam Pui King 3035870595"
date: "2021/10/31"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
# Set working Directory
setwd("C:\\Users\\jcgss\\OneDrive\\Desktop\\Master of Economics\\Sem1\\Econ 6067 2pm to 5pm Tuesday CP4- LTA\\Final Project\\1023")
```

## Covid Data
The COVID data is download from https://raw.githubusercontent.com/OxCGRT/covid-policy-tracker/master/data/OxCGRT_latest_combined.csv， air quality data in 2019-2020 and site list updated in 2021 is used.

Prepare the COVID Data

Import the raw data, keep only data in Chinese cities. This block will only be ran by one time. And then we will use the saved data file “oxdta.csv” afterwards in order to save time and simplifies the workload.

```{r }
library(readr)
oxdta <- read_csv("OxCGRT_latest_combined.csv",show_col_types = FALSE)
# keep only Chinese cities, with info and index columns.
oxdta <- oxdta[which(oxdta$CountryName=="China"),c(1:6,41,45)]
#save oxdta to save time in next manipulation
write_csv(oxdta,file="oxdta.csv")
```

## Load the COVID Data
read file “oxdta.csv” we saved before.

```{r, echo=FALSE}
library(readr)
library(data.table)
oxdta <- as.data.table(read_csv("oxdta.csv",show_col_types = FALSE))
```

## Import the Air Quality Data
Data site: https://quotsoft.net/air/

Prepare Air data
Loop to Read Air Quality Data

We have the site lists and daily air quality data in two years (2019-2020) from the source as raw data. We first create a sequence of dates which is the range of daily data we need, and then use it as i in the loop to read the files by each day. In the process, we only keep the 6 types, since we only wants the average 24h levels of pollutants and AQI, which are the 6 metrics in measuring the air quality. And correspondingly, only one moment data is needed. We choose hours = 12 for convenience.

```{r import, echo=FALSE}
# create a list of dates that we want to cover, depends on the specific time bandwidth 
dte <- format(seq(as.Date("2019-05-29"), as.Date("2020-12-31"), by="days"),format="%Y%m%d")

# import the data files
airdta <- data.table()
for (i in dte){
  # subset data with hour=12 and type within only AQI and 24 average pollutant level.
  newdta <- as.data.table(read_csv(paste0("sites.nosync/china_sites_",i,".csv"),show_col_types = FALSE))[hour==12][type %in% c("AQI","PM2.5_24h","PM10_24h","SO2_24h","NO2_24h","CO_24h")] 
  airdta <- rbind(airdta,newdta,fill=TRUE)
}
save(airdta,file="airdta.Rdata")
```

## Deal with Missing Dates

```{r missing, echo=FALSE}
# read air data
load("airdta.Rdata")

# Check missing dates
mislist <- vector()
for (i in dte){
  if (i %in% airdta$date) {
    next
  } else{
    mislist <- append(mislist,i)
  }
}

# View missing dates
list(mislist)
length(mislist)

# fill the missing dates with data of t-1
for(i in mislist){
  # copy t-1 values. Directly use math method no 1st day in missing dates.
  apnd <- airdta[which(airdta$date==as.numeric(i)-1),]
  # change the date
  apnd$date <- i
  airdta <- rbind(airdta,apnd)
}

# checks for missing dates again
nrow(airdta)/6==length(dte) # should return TRUE

save(airdta,file="airdta.Rdata")
```

## Calculate the Pollutants’ Value by City
Then pair the sites to cities, calculate the average pollutants by city and combine the new data together, save as file=airavg.Rdata for further use.

```{r calculate, echo=FALSE}
load('airdta.Rdata')

# import site list
library(readr)
sitelist <- as.data.frame(read_csv("siteslist2021.csv",show_col_types = FALSE))[,c(1,3)]

# change row names in English
names(sitelist) <- c("site", "city_CH")

# prepare empty data frame
airavg <-data.frame() 

# copy dte from previous chunk
dte <- format(seq(as.Date("2019-05-29"), as.Date("2020-12-31"), by="days"),format="%Y%m%d")

# loop each dates
for (i in dte){

  # prepare empty temporary data frame
  temp <- data.frame()
  
  #transform the table from columns to rows
  temp <- as.data.frame(t(
    rbind("r"=c("site",names(airdta)[-c(1,2,3)]),
          airdta[which(airdta$date==as.numeric(i)),][,c(-1,-2)])
    ))[-1,]
  
  # rename the columns
  names(temp) <- c('site','AQI','PM2.5_24h','PM10_24h','SO2_24h','NO2_24h','CO_24h')
  
  # add the date column with current loop value i
  temp <- cbind(temp,"date"=i)
  
  # pair cities with sites
  temp <- merge(temp,sitelist,all.x=TRUE)

  # create distinct city list in temp$city_CH
  citylist <- unique(temp$city_CH)
  
  for (i in citylist){
  
    # slice temp by city
    m <- temp[which(temp$city_CH==i),]
    
    # calculate mean by city, form 1 row data
    temp1 <- data.frame(
      "city_CH"=i,
      "AQI"=mean(as.numeric(m$AQI),na.rm=TRUE),
      "PM2.5_24h"= mean(as.numeric(m$PM2.5_24h),na.rm=TRUE),
      "PM10_24h"=mean(as.numeric(m$PM10_24h),na.rm=TRUE),
      "SO2_24h"=mean(as.numeric(m$SO2_24h),na.rm=TRUE),
      "NO2_24h"=mean(as.numeric(m$NO2_24h),na.rm=TRUE),
      "CO_24h"=mean(as.numeric(m$CO_24h),na.rm=TRUE),
      "date"=as.numeric(m$date)[1]
    )
    
    # combine in airavg
    airavg <- rbind(airavg,temp1)
  }

}
save(airavg,file="airavg.Rdata")
```

## Covid with Air Data
Combine COVID Data with Air Data Combine COVID data with air quality data, pair key index airavg$province=oxdta$region name This step was conducted in python. Please refer to my Python File.

## Calculate the Pollutants’ Value by Province Calculate the average of province.
Form file=dta.Rdata for RDD regression use.

```{r, echo=FALSE}
# load the matched Combine_Covid_data_and_Air_data from groupmates.
mtch <- as.data.frame(read_csv("Combine_Covid_data_and_Air_data.csv",show_col_types = FALSE))[,c(-1,-2)]

# get province list
names(mtch)[14] <- "province"   # rename the province column
provincelist <- na.omit(unique(mtch$province))  # omit NA (country level COVID data)

# define time range with bandwidth 90 days after lock-down which is the end of January.
dte1 <- format(seq(as.Date("2020-01-01"), as.Date("2020-04-30"), by="days"),format="%Y%m%d")

# prepare empty data frame
dta <- data.frame()

# loop to form new average data frame
for (b in dte1){
  
  # prepare empty temporary data frame
  temp <- data.frame()
  
  # subset the table by dates
  temp <- mtch[which(mtch$Date==as.numeric(b)),]
   
  # loop by province
  for (i in provincelist){
    
    # prepare empty temporary data frame
    temp2 <- data.frame()
    
    # subset the table by province
    temp1 <- temp[which(temp$province==i),-7]
    
    temp2 <- data.frame(
      "RegionName"=temp1$RegionName[1],
      "Date"=temp1$Date[1],
      "StringencyIndex"=temp1$StringencyIndex[1],
      "province" = i,
      "AQI"=mean(as.numeric(temp1$AQI),na.rm=TRUE),
      "PM2.5_24h"= mean(as.numeric(temp1$PM2.5_24h),na.rm=TRUE),
      "PM10_24h"=mean(as.numeric(temp1$PM10_24h),na.rm=TRUE),
      "SO2_24h"=mean(as.numeric(temp1$SO2_24h),na.rm=TRUE),
      "NO2_24h"=mean(as.numeric(temp1$NO2_24h),na.rm=TRUE),
      "CO_24h"=mean(as.numeric(temp1$CO_24h),na.rm=TRUE)
    )
    
    dta <- rbind(dta,temp2)
  }

}
save(dta,file="dta.Rdata")
```

## Analysis Using RDD
Manage dta
Add the air data before from 2019-09-01 to 2019-12-31
Add column dummy variable
Trans the date form
Add threshold date difference.

```{r , echo=FALSE}
load('dta.Rdata')

# add treatment dummy in dta
dta <- cbind(dta,"treatment"=ifelse(dta$StringencyIndex==0,0,1))

# trans date form use as.Date
dta$Date <- as.Date(as.character(dta$Date),format="%Y%m%d")

# add threshold date in dta
dta <- cbind(dta,"threshold"=as.numeric((dta$Date-as.Date("20200123",format="%Y%m%d"))))

save(dta,file="dta.Rdata")
```

## The model
* Please refer to the paper for the actual model, the notation has been changed for displaying convenience here.

AirMetricsit=TREATMENTit+THRESHOLDit+eit

```{r , echo=FALSE}
load('dta.Rdata')
dta <- dta[which(dta$threshold<22),]

# OLS model
library(memisc) 

metrics <- names(dta)[5:10]
mlist <- list()
m1_AQI<- lm(AQI~treatment+threshold+treatment*threshold,data=dta)
m2_AQI <- lm(AQI~treatment+threshold,data=dta)

m1_PM2.5_24h<- lm(PM2.5_24h~treatment+threshold+treatment*threshold,data=dta)
m2_PM2.5_24h <- lm(PM2.5_24h~treatment+threshold,data=dta)

m1_PM10_24h<- lm(PM10_24h~treatment+threshold+treatment*threshold,data=dta)
m2_PM10_24h <- lm(PM10_24h~treatment+threshold,data=dta)

m1_SO2_24h<- lm(SO2_24h~treatment+threshold+treatment*threshold,data=dta)
m2_SO2_24h <- lm(SO2_24h~treatment+threshold,data=dta)

m1_NO2_24h<- lm(NO2_24h~treatment+threshold+treatment*threshold,data=dta)
m2_NO2_24h <- lm(NO2_24h~treatment+threshold,data=dta)

m1_CO_24h<- lm(CO_24h~treatment+threshold+treatment*threshold,data=dta)
m2_CO_24h <- lm(CO_24h~treatment+threshold,data=dta)

mtable(m1_AQI,m2_AQI,m1_PM2.5_24h,m2_PM2.5_24h,m1_PM10_24h,m2_PM10_24h,m1_SO2_24h,m2_SO2_24h,m1_NO2_24h,m2_NO2_24h,m1_CO_24h,m2_CO_24h)


```

```{r , echo=FALSE}
load('dta.Rdata')
dta <- dta[which(dta$threshold<22),]

# install.packages("rdd")
# install.packages("rddtools")
library("rdd")
library("rddtools")
library("dplyr")
library("ggplot2")


rdd_data(y = dta$PM2.5_24h, 
         x = dta$StringencyIndex, 
         cutpoint = 40) %>% 
  rdd_reg_lm(slope = "same") %>% 
  summary()

rdd_data(y = dta$PM2.5_24h, 
         x = dta$StringencyIndex, 
         cutpoint = 40) %>% 
  rdd_reg_lm(slope = "separate", order = 2) %>% 
  summary()

# graph for 6 air quality metrics
dta %>% #AQI
  select(StringencyIndex, AQI) %>%
  mutate(treatment = as.factor(ifelse(StringencyIndex >= 40, 1, 0))) %>%
  ggplot(aes(x = StringencyIndex, y = AQI, color = treatment)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x ^ 2),
              se = FALSE) +
  scale_color_brewer(palette = "Accent") +
  guides(color = FALSE) +
  geom_vline(xintercept = 40, color = "red",
    size = 1, linetype = "dashed") +
  labs(y = "AQI",
       x = "StringencyIndex(0-100)")
  ggsave(filename="AQI.jpg")


dta %>% #PM2.5_24h
  select(StringencyIndex, PM2.5_24h) %>%
  mutate(treatment = as.factor(ifelse(StringencyIndex >= 40, 1, 0))) %>%
  ggplot(aes(x = StringencyIndex, y = PM2.5_24h, color = treatment)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x ^ 2),
              se = FALSE) +
  scale_color_brewer(palette = "Accent") +
  guides(color = FALSE) +
  geom_vline(xintercept = 40, color = "red",
    size = 1, linetype = "dashed") +
  labs(y = "PM2.5_24h",
       x = "StringencyIndex(0-100)")
  ggsave(filename="PM2.5_24h.jpg")

dta %>% #PM10_24h
  select(StringencyIndex, PM10_24h) %>%
  mutate(treatment = as.factor(ifelse(StringencyIndex >= 40, 1, 0))) %>%
  ggplot(aes(x = StringencyIndex, y = PM10_24h, color = treatment)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x ^ 2),
              se = FALSE) +
  scale_color_brewer(palette = "Accent") +
  guides(color = FALSE) +
  geom_vline(xintercept = 40, color = "red",
    size = 1, linetype = "dashed") +
  labs(y = "PM10_24h",
       x = "StringencyIndex(0-100)")
  ggsave(filename="PM10_24h.jpg")

dta %>% #SO2_24h
  select(StringencyIndex, SO2_24h) %>%
  mutate(treatment = as.factor(ifelse(StringencyIndex >= 40, 1, 0))) %>%
  ggplot(aes(x = StringencyIndex, y =SO2_24h, color = treatment)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x ^ 2),
              se = FALSE) +
  scale_color_brewer(palette = "Accent") +
  guides(color = FALSE) +
  geom_vline(xintercept = 40, color = "red",
    size = 1, linetype = "dashed") +
  labs(y = "SO2_24h",
       x = "StringencyIndex(0-100)")
  ggsave(filename="SO2_24h.jpg")

dta %>% #NO2_24h
  select(StringencyIndex, NO2_24h) %>%
  mutate(treatment = as.factor(ifelse(StringencyIndex >= 40, 1, 0))) %>%
  ggplot(aes(x = StringencyIndex, y =NO2_24h, color = treatment)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x ^ 2),
              se = FALSE) +
  scale_color_brewer(palette = "Accent") +
  guides(color = FALSE) +
  geom_vline(xintercept = 40, color = "red",
    size = 1, linetype = "dashed") +
  labs(y = "NO2_24h",
       x = "StringencyIndex(0-100)")
  ggsave(filename="NO2_24h.jpg")

dta %>% #CO_24h
  select(StringencyIndex, CO_24h) %>%
  mutate(treatment = as.factor(ifelse(StringencyIndex >= 40, 1, 0))) %>%
  ggplot(aes(x = StringencyIndex, y =CO_24h, color = treatment)) +
  geom_point() +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x ^ 2),
              se = FALSE) +
  scale_color_brewer(palette = "Accent") +
  guides(color = FALSE) +
  geom_vline(xintercept = 40, color = "red",
    size = 1, linetype = "dashed") +
  labs(y = "CO_24h",
       x = "StringencyIndex(0-100)")
  ggsave(filename="CO_24h.jpg")
```


